Study protocol

### 2022-02-01 Manuscript/S1.Protocol.Rmd
minor edit
update "New search session" section

## Acquisition of the records

@@

Once the new query was generated, a second search session called `Session2` was created, using the strategy described in the protocol.
Due to the lower specificity of the second query, particular care may be needed in managing the far larger amount of records:
multiple record files may need to be downloaded from Pubmed, EMBASE, and SCOPUS since they have limits on the number of records one can download at once;
also, the machine learning classification processing time increases proportionally with the number of records to label.\
It is advisable to consider removing the less specific rules iteratively from the new query until a manageable number of records is obtained, considering that the probability of finding new positive matches not already found by more specific queries drops exponentially.\

Once the new records are collected, `enrich_annotation_file('Session2')` (or any other new session name) can be used to perform the new CR iterations.
It may be possible that during the first CR iteration, the number of records requiring manual review is significant:
we suggest evaluating still not more than 250, keeping in mind to set the `stop_on_unreviewed` argument to `FALSE`.

>>>>

## Acquisition of the citaion data

@@

Once the new query was generated, a second search session can be created, using the strategy described in the protocol.
Due to the lower specificity of the second query, particular care may be needed in managing the far larger amount of records:
multiple record files may need to be downloaded from Pubmed, EMBASE, and SCOPUS since they have limits on the number of records one can download at once;
also, the machine learning classification processing time increases proportionally with the number of records to label.\
It is advisable to consider removing the less specific rules iteratively from the new query until a manageable number of records is obtained, considering that the probability of finding new positive matches not already found by more specific queries drops exponentially.\

Once the new records are collected are manually collected for databases without an API access, a new search can be performed. The following code describe how to create a new session. Keep in mind to give the session a new name and to import the annotated records from the last session when generating the new annotation file.

```{r new annotation session}

# Repeat the search with the new query, giving a different Session name not to
# override previous records
journal <- perform_search_session(
	query = query, year_query = year_filter,
	session_name = 'Session2', query_name = 'Query1',
	records_folder = 'Records',
	journal = 'Session_journal.csv')

# Get the path to the annotated data in the previous session
previousAnnotations <- get_session_files('Session1')$Annotations %>% last()

# Create the new annotation file passing the folder with the new records
Annotation_data <- create_annotation_file(
	file.path('Records', 'Session2'),
	reorder_query = query,
	prev_records = previousAnnotations
)

# Create the new annotation session
create_session(Annotation_data, session_name = "Session2")

Once the new annotation session data is created, `enrich_annotation_file('Session2')` can be used to perform the CR iterations.
It may be possible that during the first CR iteration, the number of records requiring manual review is very large:
we suggest evaluating still not more than 250, setting the `stop_on_unreviewed` argument to `FALSE` to proceed in the automatic classification even if some uncertain records from the precedent iteration are still unreviewed.
